plyranges: a grammar for manipulating genomics data

### 2018-02-12 README.Rmd
move outline into README

---
title: Outline of plyranges a grammar of genomic data manipulation
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
bibliography: references.bib
link-citations: true

---

>>>>

---
output: github_document
bibliography: references.bib
link-citations: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# plyranges-paper
